Appendix 3: Estimating species interactions

### 2015-08-05 Harris_2015/recovery.tex
submitted to Ecology

\begin{verbatim}
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0302 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0189 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0172 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0461 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0297 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0326 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0165 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0315 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.021 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0126 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0942 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0302 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0281 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0199 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0156 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0256 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0323 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0293 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0253 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0283 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0165 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0125 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0221 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0426 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0403 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0353 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0224 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0238 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0326 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0149 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0132 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0169 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0364 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0322 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0377 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.009 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0213 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.018 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.034 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0255 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0321 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0147 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0161 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0253 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0121 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0166 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0235 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0237 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0358 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0173 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0532 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1276 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.311 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.3631 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.2586 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1348 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1437 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.3609 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0889 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1302 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0517 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1508 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1163 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1135 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1597 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.2075 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1392 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.459 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1726 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1095 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1174 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1909 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1924 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.2261 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1249 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.159 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1499 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1224 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1935 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.2215 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1248 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1337 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0892 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1546 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.0723 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1481 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1154 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1386 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1158 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1681 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1362 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.2259 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1116 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.12 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1533 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1226 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1985 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.3044 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1416 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.1534 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.3426 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.7236 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.5589 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.4883 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6616 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.7645 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.494 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.7008 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.3284 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6008 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6168 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.4011 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.3676 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.2673 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6011 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6675 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6813 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.4592 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6586 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6237 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.3866 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.4468 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.767 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6031 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.851 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6081 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.5805 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.5058 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.4585 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6108 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.4147 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.5198 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.4652 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6374 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.4167 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6822 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.3729 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.5584 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.5641 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.7974 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.7246 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.5429 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6172 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6817 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.5112 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.6673 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.7543 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.755 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.7918 
## 
## Estimating optimal shrinkage intensity lambda (correlation matrix): 0.7204
\end{verbatim}

@@

\begin{verbatim}
##           BayesComm               Pairs   partial BayesComm 
##                12.7                15.4                18.5 
##         correlation partial correlation                 GLM 
##                18.6                27.5                29.9 
##      Markov network 
##                34.6
\end{verbatim}

@@

\begin{verbatim}
## correlation   BayesComm       Pairs 
##        1.00        0.79       -0.92
\end{verbatim}

@@

\begin{verbatim}
## R-squared is 1.23-1.29 times higher than from partial correlation (95% bootstrap CI)
## R-squared is 1.77-1.95 times higher than from correlation (95% bootstrap CI)
## R-squared is 1.14-1.18 times higher than from GLM (95% bootstrap CI)
## R-squared is 2.54-2.9 times higher than from BayesComm (95% bootstrap CI)
## R-squared is 1.77-1.97 times higher than from partial BayesComm (95% bootstrap CI)
## R-squared is 2.12-2.38 times higher than from Pairs (95% bootstrap CI)
\end{verbatim}

>>>>

@@

\begin{verbatim}
##           BayesComm               Pairs         correlation 
##                11.6                15.4                18.6 
##   partial BayesComm partial correlation                 GLM 
##                26.1                27.5                29.9 
##      Markov network 
##                34.6
\end{verbatim}

@@

\begin{verbatim}
## correlation   BayesComm       Pairs 
##        1.00        0.85       -0.92
\end{verbatim}

@@

\begin{verbatim}
## R-squared is 1.23-1.29 times higher than from partial correlation (95% bootstrap CI)
## R-squared is 1.79-1.95 times higher than from correlation (95% bootstrap CI)
## R-squared is 1.14-1.18 times higher than from GLM (95% bootstrap CI)
## R-squared is 2.72-3.28 times higher than from BayesComm (95% bootstrap CI)
## R-squared is 1.29-1.37 times higher than from partial BayesComm (95% bootstrap CI)
## R-squared is 2.12-2.37 times higher than from Pairs (95% bootstrap CI)
\end{verbatim}
